---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# SrealityAnalyzer

<!-- badges: start -->
<!-- badges: end -->

The goal of SrealityAnalyzer is to ...

## Installation

You can install the released version of SrealityAnalyzer from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("SrealityAnalyzer")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Giannettig/SrealityAnalyzer")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(SrealityAnalyzer)
library(urltools)
library(dplyr)
## basic example code

url_prodej<-"https://www.sreality.cz/hledani/prodej/byty/ustecky-kraj,karlovarsky-kraj,stredocesky-kraj"
url_pronajem<-"https://www.sreality.cz/hledani/pronajem/byty/ustecky-kraj,karlovarsky-kraj,stredocesky-kraj"

#takhle nastavím parametry v adrese
url<- urltools::param_set(url_prodej, key = "bez-aukce", value = "1")%>%
      urltools::param_set( key = "vlastnictvi", value = "osobni")%>%
      urltools::param_set( key = "stari", value = "tyden")%>%
      urltools::param_set( key = "strana", value = "14")

byty_prodej_7dni<-rvest::read_html(url)
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/master/examples>.

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
